A Comparison of Dimensionality Reduction Techniques for Robotic Motion Planning

### 2016-05-13 paper/paper.tex
made plots huge

We implemented an n-dimensional world in which to test these algorithms. We
structured our code so that we could run our tests in any space of dimension $d
\geq 2$. We also made visualization scripts for the 2- and 3-dimensional tests
(examples of which can be seen in Figs~\ref{fig:2d_examples}
and~\ref{fig:3d_examples}).

@@

\begin{figure}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{2d_example_1.pdf}
        \caption{a}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{2d_example_2.pdf}
        \caption{b}
    \end{subfigure}
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{2d_example_3.pdf}
        \caption{c}
    \end{subfigure}
    \caption{2d examples}
    \label{fig:2d_examples}
\end{figure}

\begin{figure}[t!]
    \centering
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{3d_example_1.pdf}
        \caption{a}
    \end{subfigure}%
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{3d_example_2.pdf}
        \caption{b}
    \end{subfigure}
    \begin{subfigure}[t]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{3d_example_3.pdf}
        \caption{c}
    \end{subfigure}
    \caption{3d examples}
    \label{fig:3d_examples}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{plots}
    \caption{Figure}
\end{figure}

You can see examples of our code running in Fig~\ref{fig:3d_examples}. The
results are listed in Figure WHAT. They show that

>>>>

\subsection{Experimental Setup}

We implemented an n-dimensional world in which to test these algorithms. We
structured our code so that we could run our tests in any space of dimension $d
\geq 2$. We also made visualization scripts for the 2 and 3 dimensional tests.
Examples of randomly generated 2D and 3D scenes with candidate solution paths
can be seen in Fig.~\ref{fig:examples}.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{2d_example_1.pdf}
    \includegraphics[width=0.32\textwidth]{2d_example_2.pdf}
    \includegraphics[width=0.32\textwidth]{2d_example_3.pdf} \\
    \includegraphics[width=0.32\textwidth]{3d_example_1.pdf}
    \includegraphics[width=0.32\textwidth]{3d_example_2.pdf}
    \includegraphics[width=0.32\textwidth]{3d_example_3.pdf}
    \caption{Examples of paths found in 2D and 3D scenes of random obstacles
    using the PRM algorithm. The green and red circles indicate the initial
    and goal configurations respectively. The blue path indicates the candidate
    solution through the space that connects the initial and goal
    configurations.}
    \label{fig:examples}
\end{figure}

\begin{figure}[h!]
    \centering
    \makebox[\textwidth][c]{\includegraphics[width=1.5\textwidth]{plots}}
    \caption{Figure}
\end{figure}

You can see examples of our code running in Fig.~\ref{fig:examples}. The
results are listed in Figure WHAT. They show that
